\beginsong{Hallelujah}[by={Leonard Cohen}]

\beginverse
\chordson
I’ve \[A]heard there was \[A/G#]a \[F#m]secret chord,
\[F#m/G#]that \[A]David played \[A/G#]and it \[F#m]pleased the Lord
but \[D]you don’t really \[E]care for music \[A]do you?\[E]
It \[A]goes like this -- the \[D]fourth, the \[E]fifth,
the \[F#m]minor fall, the \[D]major lift,
the \[E]baffled King com\[C#]posing Halle\[F#m]lujah.
Halle\[D]lujah, halle\[F#m]lujah, halle\[D]lujah, halle\[A]\[E]lu\[A]jah. \[E]
\endverse

\beginverse
\chordsoff
Your faith was strong but you needed proof,
you saw her bathing on the roof,
her beauty in the moonlight overthrew you.
She tied you to a kitchen chair,
she broke your throne, she cut your hair
and from your lips she drew the hallelujah.
Hallelujah, hallelujah, hallelujah, hallelujah.
\endverse

\beginverse
\chordsoff
Maybe I’ve been here before,
I know this room, I’ve walked this floor,
I used to live alone before I knew you.
I’ve seen your flag on the marble arch,
love is not a victory march,
it’s a cold and it’s a broken hallelujah.
Hallelujah, hallelujah, hallelujah, hallelujah.
\endverse

\beginverse
\chordsoff
There was a time when you let me know
what’s real and going on below
but now you never show it to me, do you?
And remember when I moved in you,
the holy dove was moving too
and every breath we drew was hallelujah.
Hallelujah, hallelujah, hallelujah, hallelujah.
\endverse

\beginverse
\chordsoff
Maybe there’s a God above
and all I ever learned from love
was how to shoot at someone who outdrew you.
And it’s not a cry you can hear at night,
it’s not somebody who’s seen the light,
it’s a cold and it’s a broken hallelujah.
Hallelujah, hallelujah, hallelujah, hallelujah.
\endverse

\beginverse
\chordsoff
You say I took the name in vain,
I don't even know the name
but if I did, well really, what's it to you?
There's a blaze of light in every word,
it doesn't matter which you heard
the holy or the broken Hallelujah.
Hallelujah, hallelujah, hallelujah, hallelujah.
\endverse

\beginverse
\chordsoff
I did my best, it wasn't much,
I couldn't feel, so I tried to touch,
I've told the truth, I didn't come to fool you.
And even though it all went wrong,
I'll stand before the Lord of Song
with nothing, nothing on my tongue but hallelujah.
Hallelujah, hallelujah, hallelujah, hallelujah.
\endverse
\endsong
