\beginsong{I Dont Know How To Love Him}[by={Andrew Lloyd Webber}]

\beginverse
\chordson
\[D]I \[G]don't \[D]know how to \[G]love \[D]him.
\[G]What to \[G6]do, \[G]how to \[D/A]move \[A]him.
I've been \[D/F#]changed, \[A]yes really \[D]changed. \[A]
In these \[F#mi7]past few \[Hmi]days when I've \[F#mi7]seen my\[Hmi]self,
I \[G]seem \[D/F#]like \[Emi]some\[D]one \[A9sus]else. \[A]
\endverse

\beginverse
\chordson
\[D]I \[G]don't \[D]know how to \[G]take \[D]this,
\[G]I don't \[G6]see \[G]why he \[D/A]moves \[A]me.
He's a \[D/F#]man, \[A]he's just a \[D/F#]man
and I've \[F#mi7]had so \[Hmi]many \[F#mi7]men be\[Hmi]fore
in \[G]ve\[D/F#]ry \[Emi]ma\[D]ny \[A9sus]ways, \[A]
\[G]he's \[D/F#]just \[Emi]one \[D]more.
\endverse

\beginrefrain
\chordson
\[G]Should I bring him do\[F#7]wn, should I scream and sho\[Hmi]ut,
should I \[Hmi/A]speak of lo\[G]ve, let my feelings o\[D/A]ut?
I never \[C]thought I'd \[G]come to th\[D]is,
\[G]what's it \[D/F#]all a\[Emi]bout? \[A9sus] \[A]
\endrefrain

\beginverse
\chordson
\[D]Don't you \[G]think \[D]it's rather \[G]fun\[D]ny,
\[G]I should \[G6]be in \[G]this po\[D/A]si\[A]tion?
I'm the \[D/F#]one \[A]who's always \[D]been \[A]
so \[F#mi7]calm, so \[Hmi7]cool, \[Fmi7]no lover's \[Hmi7]fool
\[G]run\[D/F#]ning \[Emi]eve\[D]ry \[A9sus]show, \[A]
\[G]he \[D/F#]scares \[Emi]me \[D]so.
\endverse
\emptyrefrain

\beginverse
\chordson
\[D]Yet, \[G]if \[D]he said he \[G]loved \[D]me,
\[G]I'd be \[G6]lost, \[G]I'd be \[D/A]frigh\[A]tened.
I couldn't \[D/F#]cope, \[A]just couldn't \[D]cope,\[A]
I'd \[F#mi7]turn my \[Hmi7]head, \[F#mi7]I'd back a\[Hmi7]way,
I \[G]would\[D/F#]n't \[Emi]want \[D]to \[A9sus]know, \[A]
\[G]he \[D/F#]scares \[Emi]me \[D]so, \[G]I \[D/F#]want \[Emi]him \[D]so, \[G]I \[D/F#]love \[Emi]him \[D]so.
\endverse
\endsong
